Results

### 2021-09-17 Manuscript/Manuscript_Methods.Rmd
update

---
title: "Methods"
date: "`r lubridate::today()`"
bibliography: references.bib
csl: apa.csl
output:
  # pdf_document:
  #   includes:
  #     in_header: header.tex
  github_document: default
---

@@

The automatic classification task and the manual review step form an iterative loop (CR iterations). The whole algorithm falls in the pattern defined as active machine learning [@settles2009active], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
The CR iterations continue until no new positive matches are found in four consecutive iterations. The framework supports alternative stopping conditions like limits on the fraction or number of total records reviewed and on the total number of positive matches found.

@@

### Hyperparameter search
The machine learning model behind the algorithm has a number of hyperparameters in addition to the BART specific ones: the number of ensemble models, the source of randomness between models (just derived from MCMC sampling, the default, or whether to bootstrap the data first), the oversampling of positive records, the PrI quantiles, the number of initial manually labelled records. These parameters have a relevant effect on the algorithm performance.\
We set up a grid search to evaluate the parameters on a subset made of the first 1200 records from the first session; these records were fully labelled as relevant or not. We run the framework for each combination of parameter values, automatizing the manual review part using the already collected labels. The framework ran until four CR iterations with no positive records were returned, or the whole dataset was labelled.\
For each combination, a performance score was computed as the product of *Efficiency* (number of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives). We then identified homogeneous "performance clusters" of parameter values using a decision tree on the score. For the final analysis, we chose the best cluster of parameter value combinations and, inside the cluster, the best combination in order of Sensitivity and Efficiency.

>>>>

---
title: "Methods"
date: "`r lubridate::today()`"
bibliography: references.bib
csl: apa.csl
output:
  pdf_document:
    includes:
      in_header: header.tex
  github_document: default
---

@@

The automatic classification task and the manual review step form an iterative loop (CR iterations). The whole algorithm falls in the pattern defined as active machine learning [@settles2009active, miwa2014reducing], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
The CR iterations continue until no new positive matches are found in four consecutive iterations. The framework supports alternative stopping conditions like limits on the fraction or number of total records reviewed and on the total number of positive matches found.

@@

### Hyperparameter search
The machine learning model behind the algorithm has a number of hyperparameters in addition to the BART specific ones: the number of ensemble models, the source of randomness between models (just derived from MCMC sampling, the default, or whether to bootstrap the data first), the oversampling of positive records, the PrI quantiles, the number of initial manually labelled records. These parameters have a relevant effect on the algorithm performance.\
We set up a grid search to evaluate the parameters on a subset made of the first 1200 records from the first session; these records were fully labelled as relevant or not. We run the framework for each combination of parameter values, automatizing the manual review part using the already collected labels. The framework ran until four CR iterations with no positive records were returned, or the whole dataset was labelled.\
For each combination, a performance score was computed as the product of *Efficiency* (1 minus the number of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives). We then identified homogeneous "performance clusters" of parameter values using a decision tree on the score. For the final analysis, we chose the best cluster of parameter value combinations and, inside the cluster, the best combination in order of Sensitivity and Efficiency.

### 2021-09-17 Manuscript/Manuscript_Results.Rmd
update

Figure 1 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query. As confirmed by the high efficiency values reported in Table 3, it is striking how many more records would need to be evaluated manually to find all positive matches without using a smart search tool. The engine was able to find matches even close to the end of the heuristically ordered list of records.
Specifically, in session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.\
In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows very large, even a small probability can translate, in the worst scenario, into a relevant number of predicted positive matches (`r Performance$s2$pred_positives %>% max()` in this case). To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no actual positive matches.

>>>>

Figure 2 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query. As confirmed by the high efficiency values reported in Table 3, it is striking how many more records would need to be evaluated manually to find all positive matches without using a smart search tool. The engine was able to find matches even close to the end of the heuristically ordered list of records.
Specifically, in session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.\
In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows very large, even a small probability can translate, in the worst scenario, into a relevant number of predicted positive matches (`r Performance$s2$pred_positives %>% max()` in this case). To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no actual positive matches.
